---
title: 'Question 1: Insights into the Covid 19 pandemic'
documentclass: elsarticle
Thesis_FP: no
output:
  html_document:
    df_print: paged
  pdf_document:
    keep_tex: yes
    template: Tex/TexDefault.txt
    fig_width: 3.5
    fig_height: 3.5
Author1: Pablo Rees^[__Contributions:__  \newline _The authors would like to thank
  the Kommetjie municipality for today's water outage. Thank you sincerely._]
Ref1: Stellenbosch Economics Department
Email1: 19119461\@sun.ac.za
BottomRFooter: \footnotesize Page \thepage
addtoprule: yes
addfootrule: yes
margin: 2.3
bottom: 2
top: 2.5
HardSet_layout: yes
linenumbers: no
bibliography: Tex/ref.bib
csl: Tex/harvard-stellenbosch-university.csl
RemovePreprintSubmittedTo: yes
Journal: Journal of Finance
toc: no
numbersections: yes
fontsize: 11pt
linestretch: 1.2
link-citations: yes
AddTitle: yes
abstract: |
  London has bad weather on the condition that you find cold and wet weather to be bad. 
---

<!-- First: Set your default preferences for chunk options: -->

<!-- If you want a chunk's code to be printed, set echo = TRUE. message = FALSE stops R printing ugly package loading details in your final paper too. I also suggest setting warning = FALSE and checking for warnings in R, else you might find ugly warnings in your paper. -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')
# Note: Include = FALSE implies the code is executed, but not printed in your pdf.
# warning and message = FALSE implies ugly messages and warnings are removed from your pdf.
# These should be picked up when you execute the command chunks (code sections below) in your rmd, not printed in your paper!

# Lets load in example data, and see how this can be stored and later called from your 'data' folder.
if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)

library(tidyverse)
library(readr)
library(dplyr)
library(knitr)
library(lubridate)
library(plotly)

rm(list = ls())


list.files('/Users/pablo/Desktop/DS_Test/Solution/19119461/Question2/code/', full.names = T, recursive = T) |>  as.list() |>  walk(~source(.))

weatherDf <-  read.csv(glue::glue(getwd(),'/data/london_weather.csv')) |> 
    mutate(date = lubridate::ymd(date)) |> mutate(month = lubridate::month(date,label = T),
                                          year = lubridate::year(date))





# Notice that as you are working in a .Rproj file (I am assuming you are) - the relative paths of your directories start at your specified root.
# This means that when working in a .Rproj file, you never need to use getwd() - it is assumed as your base root automatically.

```


<!-- ############################## -->
<!-- # Start Writing here: -->
<!-- ############################## -->

# Introduction \label{Introduction}
London rains a lot. If you would like to get a visceral sense of this experience please listen to this 8 hour recording of the rain in london:\n
https://www.youtube.com/watch?v=1HcEkN_290Q&ab_channel=AmbientRenders. \n
If 8 hours of rain sounds like it might not be enjoyable, I suggest you move almost anywhere else.

\n\n
\newpage
The mean monthly max, min and mean temp since 1979 is plotted below. Please use the slider to ajust the year of analysis. If this looks warm to you, then London is not cold. \n\n
```{r,  warning =  FALSE, fig.align = 'center', fig.cap = "Covid Vaccines.\\label{Figure1}", fig.ext = 'png', fig.height = 5, fig.width = 7}

g <- monthlyAvTemp(weatherDf)
g


```
\newpage
\n\n
This is an animation of the levels of cloud and rain that have occured in London since 2010. Please notice that the cloud scale starts at 10. This means that the least number of cloudy days (cloud cover > 2) since 2010 has been 10. You'll notice also the high clustering to the top right. This means the weather is kak. 
```{r,  warning =  FALSE, fig.align = 'center', fig.cap = "Covid Vaccines.\\label{Figure1}", fig.ext = 'png', fig.height = 5, fig.width = 7}

g <- precip_cloud_plot(weatherDf)
g


```
\newpage
\n\n





