---
title: 'Question 1: Insights into the Covid 19 pandemic'
documentclass: elsarticle
Thesis_FP: no
output:
  html_document:
    df_print: paged
  pdf_document:
    keep_tex: yes
    template: Tex/TexDefault.txt
    fig_width: 3.5
    fig_height: 3.5
Author1: Pablo Rees^[__Contributions:__  \newline _The authors would like to thank
  the Kommetjie municipality for today's water outage. Thank you sincerely._]
Ref1: Stellenbosch Economics Department
Email1: 19119461\@sun.ac.za
BottomRFooter: \footnotesize Page \thepage
addtoprule: yes
addfootrule: yes
margin: 2.3
bottom: 2
top: 2.5
HardSet_layout: yes
linenumbers: no
bibliography: Tex/ref.bib
csl: Tex/harvard-stellenbosch-university.csl
RemovePreprintSubmittedTo: yes
Journal: Journal of Finance
toc: no
numbersections: yes
fontsize: 11pt
linestretch: 1.2
link-citations: yes
AddTitle: yes
abstract: |
  An analysis of the effects of Covid 19 follows. It was found that Africa had lower vaccination rates and an accompanying higher death rate relative to infection rates than the rest of the world. Further it was found that higher rates of smoking had a high correlation (~30%) with ICU admission rates and by extension, death rates. Finally, 
---

<!-- First: Set your default preferences for chunk options: -->

<!-- If you want a chunk's code to be printed, set echo = TRUE. message = FALSE stops R printing ugly package loading details in your final paper too. I also suggest setting warning = FALSE and checking for warnings in R, else you might find ugly warnings in your paper. -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')
# Note: Include = FALSE implies the code is executed, but not printed in your pdf.
# warning and message = FALSE implies ugly messages and warnings are removed from your pdf.
# These should be picked up when you execute the command chunks (code sections below) in your rmd, not printed in your paper!

# Lets load in example data, and see how this can be stored and later called from your 'data' folder.
if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)

library(tidyverse)
library(readr)
library(dplyr)
library(knitr)

rm(list = ls())


list.files('/Users/pablo/Desktop/DS_Test/Solution/19119461/Question1/code/', full.names = T, recursive = T) |>  as.list() |>  walk(~source(.))

weatherDf = read.csv(glue::glue(getwd(),'/data/london_weather.csv'))



getwd()


# Notice that as you are working in a .Rproj file (I am assuming you are) - the relative paths of your directories start at your specified root.
# This means that when working in a .Rproj file, you never need to use getwd() - it is assumed as your base root automatically.

```


<!-- ############################## -->
<!-- # Start Writing here: -->
<!-- ############################## -->

# Introduction \label{Introduction}
London rains a lot. If you would like to get a visceral sense of this experience please listen to this 8 hour recording of the rain in london:\n
https://www.youtube.com/watch?v=1HcEkN_290Q&ab_channel=AmbientRenders.

\n\n

\newpage
The number of vaccines administered to Africa has been significantly lower than what the rest of the world receievd. This has been widely attributed to vaccine hoarding by richer countries as well as vaccine hesitancy prevelant amongst African communities.\n
```{r,  warning =  FALSE, fig.align = 'center', fig.cap = "Covid Vaccines.\\label{Figure1}", fig.ext = 'png', fig.height = 5, fig.width = 7}





```
\newpage
\n\n



