---
title: 'Question 1: Insights into the Covid 19 pandemic'
documentclass: elsarticle
Thesis_FP: no
output:
  pdf_document:
    keep_tex: yes
    template: Tex/TexDefault.txt
    fig_width: 3.5
    fig_height: 3.5
  html_document:
    df_print: paged
Author1: Pablo Rees^[__Contributions:__  \newline _The authors would like to thank
  the Kommetjie municipality for today's water outage. Thank you sincerely._]
Ref1: Stellenbosch Economics Department
Email1: 19119461\@sun.ac.za
BottomRFooter: \footnotesize Page \thepage
addtoprule: yes
addfootrule: yes
margin: 2.3
bottom: 2
top: 2.5
HardSet_layout: yes
linenumbers: no
bibliography: Tex/ref.bib
csl: Tex/harvard-stellenbosch-university.csl
RemovePreprintSubmittedTo: yes
Journal: Journal of Finance
toc: no
numbersections: yes
fontsize: 11pt
linestretch: 1.2
link-citations: yes
AddTitle: yes
abstract: |
  An analysis of the effects of Covid 19 follows. It was found that Africa had lower vaccination rates and an accompanying higher death rate relative to infection rates than the rest of the world. Further it was found that higher rates of smoking had a high correlation (~30%) with ICU admission rates and by extension, death rates. Finally, it was found that no single country managed to increase the number of hospital beds during the pandemic - or rather, it was found that the data may have some mistakes in it. 
---

<!-- First: Set your default preferences for chunk options: -->

<!-- If you want a chunk's code to be printed, set echo = TRUE. message = FALSE stops R printing ugly package loading details in your final paper too. I also suggest setting warning = FALSE and checking for warnings in R, else you might find ugly warnings in your paper. -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')
# Note: Include = FALSE implies the code is executed, but not printed in your pdf.
# warning and message = FALSE implies ugly messages and warnings are removed from your pdf.
# These should be picked up when you execute the command chunks (code sections below) in your rmd, not printed in your paper!

# Lets load in example data, and see how this can be stored and later called from your 'data' folder.
if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)

library(tidyverse)
library(readr)
library(dplyr)
library(knitr)

rm(list = ls())


list.files('/Users/pablo/Desktop/DS_Test/Solution/19119461/Question1/code/', full.names = T, recursive = T) |>  as.list() |>  walk(~source(.))

DeathsDf <- read.csv(glue::glue(getwd(),'/data/Deaths_by_cause.csv')) 
    
CovidDf <- read.csv(glue::glue(getwd(),'/data/owid-covid-data.csv')) 

totalDf <- CovidDf |> left_join(DeathsDf,by=c('iso_code'='Code'))





# Notice that as you are working in a .Rproj file (I am assuming you are) - the relative paths of your directories start at your specified root.
# This means that when working in a .Rproj file, you never need to use getwd() - it is assumed as your base root automatically.

```


<!-- ############################## -->
<!-- # Start Writing here: -->
<!-- ############################## -->

The number of vaccines administered to Africa has been significantly lower than what the rest of the world receievd. This has been widely attributed to vaccine hoarding by richer countries as well as vaccine hesitancy prevelant amongst African communities.\n

```{r,  warning =  FALSE, fig.align = 'center', fig.cap = "Covid Vaccines.\\label{Figure1}", fig.ext = 'png', fig.height = 5, fig.width = 7}

g <- vaccinePlot(CovidDf)

g


```
\newpage
\n\n
The number of deaths relative to the number of cases is higher in Africa than it is in non-Africa, this is demonstrated in the graphs below.\n
```{r,  warning =  FALSE, fig.align = 'center', fig.cap = "Covid Deaths and Cases.\\label{Figure1}", fig.ext = 'png', fig.height = 5, fig.width = 7}

g <- deathVsCasesPlot(CovidDf)

g


```

\newpage
Regressing the number of deaths per million on the number of icu admissions per million reveals, as expected, that there is a high correlation between ICU admissions and deaths. This was done for countries with smoking data available.\n

```{r,  warning =  FALSE, fig.align = 'center', fig.cap = "Smoking regressions.\\label{Figure1}", fig.ext = 'png', fig.height = 5, fig.width = 7}

smokersDf <- smoking(CovidDf)

Death_on_ICU <- feols(totalDeathsPerMil ~ icuPerMil, data = smokersDf)
kable(etable(Death_on_ICU))

```

\n
Regressing the rate of ICU admissions on the number of female and male smokers, seperately, reveals that the rate of female smokers is a better and stronger predictor for the rate of ICU admissions. \n

```{r,  warning =  FALSE, fig.align = 'center', fig.cap = "Smoking regressions.\\label{Figure2}", fig.ext = 'png', fig.height = 5, fig.width = 7}

    ICU_on_female <- feols(icuPerMil ~  female_smokers, data = smokersDf)
    kable(etable(ICU_on_female))

    ICU_on_male <- feols(icuPerMil ~  male_smokers, data = smokersDf)
    kable(etable(ICU_on_male))
    

```
\n
Finally, regressing the rate of ICU admissions on the (evenly weighted) average rate of smokers reveals the highest correlation and the highest adjusted r-squared at a 99,9% significance level. Thus it can be said that countries with higher rates of smokers experienced increased rates of admission to ICU wards and by extension rates of death. \n
```{r,  warning =  FALSE, fig.align = 'center', fig.cap = "Smoking regressions.\\label{Figure3}", fig.ext = 'png', fig.height = 5, fig.width = 7}

    ICU_on_mean <- feols(icuPerMil ~ meanSmokers , data = smokersDf)
    kable(etable(ICU_on_mean))

```
\n\n

The following graphs compare the rate of increase in hospital facilities with the number of icu patients per million.  The global quartiles for the mean rate of hospital beds per million over time were taken and countries were divided into the four quartiles. The highest, middle and lowest 2 countries in terms quartile placement were examined for even distribution. However, this was only done for countries with data recorded in the icu admissions rate variable. According to the data the change in the number of hospital beds per thousand people is exactly zero or Na for every country indicating that no new beds were added. As such the analysis was uninteresting. However, the graphs are presented below.

\n\n
```{r,  warning =  FALSE, fig.align = 'center', fig.cap = "Hospital capacity.\\label{Figure4}", fig.ext = 'png', fig.height = 5, fig.width = 7}

g <- hospBedsPlot(CovidDf)
g

```
\n\n

Here is table depicting the change in hospital beds:
This is also the end of the document so there isn't much need to scroll to the bottom of this empty table.
\n\n
```{r,  warning =  FALSE, fig.align = 'center', fig.cap = "Hospital capacity.\\label{Figure4}", fig.ext = 'png', fig.height = 5, fig.width = 7}

change_in_beds <- CovidDf |> group_by(location) |> 
    summarize(change = (max(hospital_beds_per_thousand)-min(hospital_beds_per_thousand)))

kable(change_in_beds)

```



