---
title: 'Question 3: A quick intro to how awesome tennis is'
documentclass: elsarticle
Thesis_FP: no
output:
  html_document:
    df_print: paged
  pdf_document:
    keep_tex: yes
    template: Tex/TexDefault.txt
    fig_width: 3.5
    fig_height: 3.5
Author1: Pablo Rees^[__Contributions:__  \newline _The authors would like to thank
  the Kommetjie municipality for today's water outage. Thank you sincerely._]
Ref1: Stellenbosch Economics Department
Email1: 19119461\@sun.ac.za
BottomRFooter: \footnotesize Page \thepage
addtoprule: yes
addfootrule: yes
margin: 2.3
bottom: 2
top: 2.5
HardSet_layout: yes
linenumbers: no
bibliography: Tex/ref.bib
csl: Tex/harvard-stellenbosch-university.csl
RemovePreprintSubmittedTo: yes
Journal: Journal of Finance
toc: no
numbersections: yes
fontsize: 11pt
linestretch: 1.2
link-citations: yes
AddTitle: yes
abstract: |
  Tennis is by far the greatest of the outdoor racquet sports. I was just seven when my coach told me I should quit because of my inability to keep the ball on the court.  
---

<!-- First: Set your default preferences for chunk options: -->

<!-- If you want a chunk's code to be printed, set echo = TRUE. message = FALSE stops R printing ugly package loading details in your final paper too. I also suggest setting warning = FALSE and checking for warnings in R, else you might find ugly warnings in your paper. -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')
# Note: Include = FALSE implies the code is executed, but not printed in your pdf.
# warning and message = FALSE implies ugly messages and warnings are removed from your pdf.
# These should be picked up when you execute the command chunks (code sections below) in your rmd, not printed in your paper!

# Lets load in example data, and see how this can be stored and later called from your 'data' folder.
if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)
library(readr)
library(dplyr)
library(knitr)
library(lubridate)
library(plotly)

rm(list = ls())


list.files('/Users/pablo/Desktop/DS_Test/Solution/19119461/Question3/code/', full.names = T, recursive = T) |>  as.list() |>  walk(~source(.))


Datroot <-  glue::glue(getwd(),'/data')
matchesQualDf <-  collateData(Datroot,'matches_qual') 

matches2000Df <-  collateData(Datroot,'matches_2') 
matches1900Df <-  collateData(Datroot,'matches_1') 

matchesDateDf <- matches1900Df |> rbind(matches2000Df)
rm(matches1900Df,matches2000Df)

rankingsDf <- collateData(Datroot,'atp_rankings') 

playersDf <- read.csv(glue::glue(Datroot,'/atp_players.csv'))



# Notice that as you are working in a .Rproj file (I am assuming you are) - the relative paths of your directories start at your specified root.
# This means that when working in a .Rproj file, you never need to use getwd() - it is assumed as your base root automatically.

```


<!-- ############################## -->
<!-- # Start Writing here: -->
<!-- ############################## -->

# Introduction \label{Introduction}
This is a short discussion on the competitive nature of tennis since the 1970's. Its actually mostly just a graph.

\n\n
\newpage

The graph below shows the evolution of competitiveness over the years. It represents the mean rank that a player acheives throughout a year on the Y-axis on the (smoothed) line graph and the scatter points while the labels at the end of the lines show the ranking (by highest average annual ranking) that they represent. By this depiction, the higher the mean ranking depicted on a graph the more the rankings traded hands and thus the more competitive a year of tennis was.
 \n\n
```{r,  warning =  FALSE, fig.align = 'center', fig.cap = "Covid Vaccines.\\label{Figure1}", fig.ext = 'png', fig.height = 5, fig.width = 7}
g <- plotCompetitiveness(playersDf,rankingsDf)
g


```






